### 2014-11-12 splash-bp.tex
spacing

\begin{dblfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=5.5cm]{results/system_belief-propagation-400.png}}
      \subfloat[]{\includegraphics[width=5.5cm]{results/system_splash-bp-400.png}}
      \subfloat[]{\includegraphics[width=5.5cm]{results/system_improve_belief-propagation-400.png}}
   \end{center}
   \scap{results:splash_bp}{Experimental results for LBP and SBP. Figure (a) shows the
      scalability of LBP for both CLM and GraphLab and Figure (b) shows the
      scalability of SBP. Figure (c) presents the
      improvements seen in SBP against LBP, where SBP runs, on average, 1.5 to 2.5
      times faster than LBP.}
\end{dblfig}

>>>>

\begin{dblfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=5.5cm]{results/system_belief-propagation-400.png}}
      \subfloat[]{\includegraphics[width=5.5cm]{results/system_splash-bp-400.png}}
      \subfloat[]{\includegraphics[width=5.5cm]{results/system_improve_belief-propagation-400.png}}
   \end{center}
   \scap{results:splash_bp}{Experimental results for LBP and SBP. (a) shows the
      scalability of LBP for both CLM and GraphLab and (b) shows the
      scalability of SBP. (c) presents the
      improvements seen in SBP against LBP, where SBP runs, on average, 1.5 to 2.5
      times faster than LBP.}
\end{dblfig}
